### 2019-03-25 manuscript.tex
Update manuscript.tex

It is estimated that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East \cite{UNFPA14, UNIC16} \cfonly{updated Sep 18}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{}.  Current progress of in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jdcmt{This claim is surprising, and the sources are not
academic.}\cfcmt{UN is supposed to be reliable and often quoted by academic papers}. \jdcmt{Not all UN sources are the same. The factsheet does not even seem to say that.} Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision;
we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)) \jd{How do you see the Tostan fitting in? Or is that a cfonly thing?.

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
progress is hindered due to the complicated history of the very practice \cite{cite}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

@@

@@

Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs. no-tolerance, fgc vs. mc \cite{WahlEsse18}?  We suggest to position ourselves in a context where male circumcision (MC) is practices and accepted; to consider the differences of a prick of FGC and MC; to comprehend the outcomes of abolishing FGC vs. changing FGC practices.

@@

--- questions worth addressing
1. Is there a tipping point?  Can our findings disclose some ideas on fgc intervention in terms of behavioural change in order to reach a tipping point?
\subsection{Funding}\label{Funding}

>>>>

It is estimated, based on a UNICEF global database including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS),  and other nationally representative surveys between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East and 44 millions of them are girls below age 15 \cite{UNIC16}.  The United Nations has declared that FGC as violates human rights, and promoted the abandonment of the practice  \cite{WHO97, WHO08}.  Current progress in reducing FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next decade \cfonly{double check}) if the trends continue \cite{KhosBane17, UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18).  Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01}  \cfonly{To rethink differences between FGC and FGM.  The types of FGC vary from just a knick to a sever sewing of the genital area.  Using FGC(cutting) seems to ignore the damage to the girls and human rights, but FGM(utilization) seem harsh and biased against local cultures.  FGC(cirumcision) may be the best for current situation globally.)

The commonly shared position for FGC is more about eradication than intervention \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}; but the
progress is hindered due to the complicated history of the very practice \cite{cite}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.

@@

% To question the difference between MC and FGC if FGC can be minimized to the form of “just a knick” or type I or minor.

@@

Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs. no-tolerance, fgc vs. mc \cite{WahlEsse18}?  We suggest to position ourselves in a context where male circumcision (MC) is practices and accepted; to consider the differences of a prick of FGC and MC; to comprehend the outcomes of abolishing FGC vs. changing FGC practices.
\cite{WahlEsse18}:  from sameness to differences, a global multicultural approach especially during the international migration across the globe.

@@

--- questions worth addressing
1. Is there a tipping point?  Can our findings disclose some ideas on fgc intervention in terms of behavioural change in order to reach a tipping point?

_ Following up project:
 Threshold on FGC:  based on our finding, mother’s FGC status and community FGC prevalence is a good predictor of daughter’s future FGC status.  We can use newer DHS of multiple nations to predict the future of FGC practice.

\subsection{Funding}\label{Funding}
